---
title: "README"
author: "Lars Mølgaard Saxhaug"
date: "6/29/2021"
output: github_document
---

## Bayesian reanalysis on the basis of ["FFP3 respirators protect healthcare workers against infection  with SARS-CoV-2"](https://authorea.com/users/421653/articles/527590-ffp3-respirators-protect-healthcare-workers-against-infection-with-sars-cov-2)

```{r setup, include=FALSE}
library(tidyverse)
library(tidybayes)
library(tidylog)
library(janitor)
library(snakecase)
library(lubridate)
library(here)
library(rethinking)
library(tidybayes.rethinking)
theme_set(theme_tidybayes())
```

```{r data}
df <- tibble::tribble(
  ~Week, ~Week.start, ~Red.cases, ~Red.ward.days, ~Red.cases.per.ward.day, ~Green.cases, ~Green.ward.days, ~Green.cases.per.ward.day, ~Excluded.cases, ~Total, ~Community,
  1L, "02/11/2020", 0L, 7L, 0, 5L, 245L, 0.02, 16L, 21L, 7876L,
  2L, "09/11/2020", 2L, 7L, 0.286, 7L, 245L, 0.028, 33L, 42L, 9499L,
  3L, "16/11/2020", 1L, 12L, 0.083, 3L, 240L, 0.013, 26L, 30L, 7998L,
  4L, "23/11/2020", 1L, 14L, 0.071, 6L, 238L, 0.025, 24L, 31L, 7203L,
  5L, "30/11/2020", 3L, 14L, 0.214, 6L, 238L, 0.025, 20L, 29L, 9441L,
  6L, "07/12/2020", 5L, 14L, 0.357, 10L, 238L, 0.042, 33L, 48L, 16535L,
  7L, "14/12/2020", 1L, 14L, 0.071, 7L, 238L, 0.029, 41L, 49L, 31219L,
  8L, "21/12/2020", 3L, 14L, 0.214, 10L, 238L, 0.042, 56L, 69L, 37259L,
  9L, "28/12/2020", 2L, 21L, 0.095, 20L, 231L, 0.087, 58L, 80L, 50110L,
  10L, "04/01/2021", 4L, 29L, 0.138, 34L, 223L, 0.152, 70L, 108L, 41663L,
  11L, "11/01/2021", 5L, 50L, 0.1, 34L, 202L, 0.168, 63L, 102L, 31341L
) %>%
  rename_with(to_snake_case) %>%
  mutate(week_start = as_date(parse_date_time(week_start, orders = "dmy"))) 
# pivot longer, create stan compatible data
df_mod <- df %>%
  pivot_longer(starts_with("red") | starts_with("green"), names_to = c("ward", "variable"), names_pattern = "(\\w[^_]*)_?(.*)") %>%
  mutate(across(where(is.character), as.factor),
         community=as.numeric(community)) %>%
  pivot_wider(values_from = value, names_from = variable) %>%
  mutate(fp=as.integer(ifelse(ward=="green",1,ifelse(week<9,2,3)))) %>% select(cases,community,fp,ward_days) %>% 
  as.list()
```

#### Model sampling

k: constant for community derived infections

b: corresponding to g, r1 and r2 parameters in original paper, parameter for ward derived infections

```{r fit}
# using rethinking package to compose and sample stan model
# priors are very uninformative
m1 <- ulam(alist(
  cases ~ dpois(lambda), # poisson likelihood
  lambda <- (k * community + b[fp]) * ward_days,
  k ~ dexp(1),
  b[fp] ~ dexp(1)
), data = df_mod, chains = 4, iter = 2000, cores = 4, file = here("fits", "m1"))
precis(m1, depth = 2)
plot(m1, depth = 2)
stancode(m1)
```

#### Stancode:

```{r stancode}
rethinking::stancode(m1)
```

#### Mean and credible intervals corresponding to table 2 in the paper

```{r sample_parameters, message=FALSE}


m1 %>%
  gather_draws(k, b[fp]) %>%
  mutate(fp = factor(fp, levels = 1:4, labels = c("green", "red_pre_ffp3", "red_post_ffp3", "na"))) %>%
  mean_hdi(.value) %>%
  mutate(parameter = ifelse(.variable == "b", paste(.variable, fp, sep = "_"), .variable)) %>%
  ungroup() %>%
  select(parameter, .value, .lower, .upper) %>%
  mutate(parameter = as.character(parameter)) %>%
  bind_rows(., m1 %>%
    spread_draws(k, b[fp]) %>%
    mutate(fp = factor(fp, levels = 1:3, labels = c("b_green", "b_red_pre_ffp3", "b_red_post_ffp3"))) %>%
    compare_levels(b, by = fp, fun = `/`) %>%
    mean_hdci() %>%
    select(fp, b, .lower, .upper) %>%
    rename("parameter" = fp, ".value" = b)) %>%
  mutate(parameter = factor(parameter, levels = c(
    "k", "b_green", "b_red_pre_ffp3", "b_red_post_ffp3", "b_red_post_ffp3 / b_red_pre_ffp3", "b_red_pre_ffp3 / b_green",
    "b_red_post_ffp3 / b_green"
  ))) %>%
  arrange(parameter) %>%
  knitr::kable(col.names = c("Model parameter", "Posterior mean", "Lower bound 95% cred. int.", "Upper bound 95% cred. int"))


```

#### Posterior distributions for ward driven infection risk

```{r plot}
m1 %>% 
  spread_draws(k,b[fp]) %>% 
  mutate(fp=factor(fp,levels = 1:3,labels = c("green","red_pre_ffp3","red_post_ffp3"))) %>%
  ggplot(aes(x=b,y=fp))+
  stat_halfeye() +
  scale_x_continuous(name = "Posterior distribution for b parameter")+
  scale_y_discrete(name = NULL)

```
